A High-Level Embedded Language for Low-Level GPU Kernel Programming

### 2013-11-11 src2/hl/paperThesis.tex
update

\subsection{Fractals}

@@

\subsection{Combining kernels to solve large problems} 
\label{sec:Benchmarks}

@@

\subsection{What should the combinators be?}
In this latest version of Obsidian, we have at last got a system
that permits the construction of high performance kernels. But it is
clear that we need to think hard about the set of combinators that
we use to describe common patterns of parallel and sequential computation.
Our current choice is a bit ad hoc and needs to be generalised and made
more systematic. We will also explore the use of search to find algorithmic 
decompositions that are well matched to the GPU, exploiting the fact 
that Obsidian is embedded in a powerful host language.

>>>>

\subsubsection{Fractals}

@@

\subsubsection{Combining kernels to solve large problems} 
\label{sec:Benchmarks}

@@

\subsubsection{What should the combinators be?}
In this latest version of Obsidian, we have at last got a system
that permits the construction of high performance kernels. But it is
clear that we need to think hard about the set of combinators that
we use to describe common patterns of parallel and sequential computation.
Our current choice is a bit ad hoc and needs to be generalised and made
more systematic. We will also explore the use of search to find algorithmic 
decompositions that are well matched to the GPU, exploiting the fact 
that Obsidian is embedded in a powerful host language.
